MSAD_PCA_Walkthrough

### 2017-02-03 README.Rmd
Fixed stats::lag, zoo::zoo, and xts::xts data interaction. Without the explicit package calls, the lags are interpreted backwards. Added an escape clause to faultFilter to ensure that the number of test rows is at least the number of consecutive flags to trigger an alarm. Further, I completely re-ran all the real data import, cleaning, and analysis code from the vignette. We are still seeing all alarms for the real data. I'd like to get a lot more training observations to test with before I dig back in to the code.

# Calculate the training summary, but save five observations for monitoring.
trainResults_ls <- mspTrain(data = normal_switch_xts[1:(n - 5), -1],
                            labelVector = normal_switch_xts[1:(n - 5), 1],
                            trainObs = nTrainObs,
                            lagsIncluded = 1)

@@

# While training, we included 1 lag (the default), so we will also lag the
# observations we will test.
testObs <- normal_switch_xts[(n - 6):n, -1]
testObs <- stats::lag(testObs, 0:1)
testObs <- testObs[-1, ]
testObs <- cbind(normal_switch_xts[(n - 5):n, 1], testObs)
testObs

>>>>

# Calculate the training summary, but save five observations for monitoring.
trainResults_ls <- mspTrain(data = normal_switch_xts[1:(n - 5), -1],
                            labelVector = normal_switch_xts[1:(n - 5), 1],
                            trainObs = nTrainObs,
                            lagsIncluded = c(0, -1))

@@

# While training, we included 1 lag (the default), so we will also lag the
# observations we will test.
testObs <- normal_switch_xts[(n - 6):n, -1]
testObs <- stats::lag(zoo::zoo(testObs), 0:-1)
testObs <- xts::xts(testObs[-1,])
testObs <- cbind(normal_switch_xts[(n - 5):n, 1], testObs)
testObs
